Is it Better to be a Moose or a Black Bear?

### 2024-04-15 paper/paper.qmd
Completed data cleaning script for moose and bear data

---
title: "Analysis of Ontario Wildlife Harvests and Active Hunters"
subtitle: "2009-2023"
author: Samantha Barfoot
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction

>>>>

---
title: "Is it Better to be a Moose or a Black Bear?"
subtitle: "An Analysis of Ontario Wildlife Harvest and Active Hunter Rates From 2012 to 2023"
author: Samantha Barfoot
thanks: "Code and data are available at: https://github.com/SamanthaBarfoot/wildlife_hunting.git"
date: today
date-format: long
abstract: "This paper analyzes Ontario wildlife harvest counts, specifically moose and black bears, and the number fo active hunters based on region. The analysis examines harvest counts from 2012 to 2023 across northern, southeastern, and southwestern Ontario. It was found that..."
format: pdf
number-sections: true
table-of-contents: true
bibliography: references.bib
---
# Introduction
